\subsection{Reddit Corpus}
Reddit is an ideal corpus for asking such a question for a variety of reasons. First, Reddit is, at least partially, driven by news articles. Most Reddit submissions start with a user submitting a hyperlink. This has the added benefit of giving discussants a clear shared context.

After the submission, people can reply with their thoughts in a \textit{comment}. Users can also comment on these comments. Users can also provide feedback with Reddit's curation system. Reddit users can \textit{upvote} a comment or submission to express approval or \textit{downvote} a comment or submission to express disapproval.

Both submissions and comments are sorted by \textit{score}\footnote{While comments are hierarchical, at each level of the hierarchy, they are sorted by score.}, the number of upvotes minus the number of downvotes. If a comment is sufficiently downvoted, it will be hidden. Hidden comments can still be read, replied to, upvoted, and downvoted, but a user has to manually display hidden comments. When a comment receives both upvotes and downvotes, it is considered \textit{controversial}. In the case of armed conflicts, this is vanishingly rare: less than 1\% of comments are considered controversial.  

Reddit is organized into a highly expandable number of smaller forums, normally referred to as subreddits. Each of these subreddits can be about any given topic, general or specific. For instance, it is possible to have subreddits about science, biology, and genetics. These three subreddits can be completely independent, as they are not organized hierarchically.

Besides the organizational ways that Reddit is different than Twitter, it is also more culturally homogeneous. The vast majority of the discussions are in English. Over half of the users are in the United States, and the majority are fairly young \footnote{Source--http://www.pewinternet.org/2013/07/03/6-of-online-adults-are-reddit-users/}. Among those not in the United States, the next most contributing countries are primarily East Asian, Australasian, Western European, and Northern European\footnote{Source--http://www.redditblog.com/2013/12/top-posts-of-2013-stats-and-snoo-years.html}. 

Researchers normally investigate phenomena in a small selection of subreddits. For instance, Hurricane Sandy has a dedicated subreddit. It was used to investigate Reddit's networked gatekeeping and how it impacts the framing of a crisis situation, as the voting system forms a non-traditional mechanism for negotiating what information is relevant \cite{Leavitt}. Another study examined the sharing and seeking of mental health information to examine factors that drive social support \cite{dechoudhury2014mental}.

\subsection{Armed Conflict Database}
The Armed Conflicts Database is developed by the International Institute for Strategic Study, containing various indexes of armed conflicts around the world \cite{conflictDB}. They sort conflicts into several regions: Caribbean and the Americas, East Asia and Australasia, Europe, Middle East and North Africa, Russia and Eurasia, South Asia, and lastly, Sub-Saharan Africa. The Armed Conflict Database contains data on fatalities, IDP, and refugees from a conflict: both by year and in total. It additionally lists the year the conflict started and a variety of factors that relate to the conflict's origin, such as ethnic violence or terrorism. Lastly, they rate the current Intensity of the conflict, which can be Archived, Low, Medium, or High.




