
%%%%%%%%%%%%%%%%%%%%%%% file typeinst.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is the LaTeX source for the instructions to authors using
% the LaTeX document class 'llncs.cls' for contributions to
% the Lecture Notes in Computer Sciences series.
% http://www.springer.com/lncs       Springer Heidelberg 2006/05/04
%
% It may be used as a template for your own input - copy it
% to a new file with a new name and use it as the basis
% for your article.
%
% NB: the document class 'llncs' has its own and detailed documentation, see
% ftp://ftp.springer.de/data/pubftp/pub/tex/latex/llncs/latex2e/llncsdoc.pdf
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[runningheads,a4paper]{llncs}

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}

\usepackage{url}
\urldef{\mailsa}\path|{jrcole,ying.xu,reitter}@psu.edu|    
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

\begin{document}

\mainmatter  % start of an individual contribution

% first the title is needed
\title{How People Talk about Armed Conflicts}

% a short form should be given in case it is too long for the running head
%\titlerunning{How People Talk about Armed Conflicts}

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%
\author{Jeremy Cole
\and Ying Xu\and David Reitter}
%
%\authorrunning{Jeremy Cole, Ying Xu, and David Reitter}
% (feature abused for this document to repeat the title also on left hand pages)

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{The Pennsylvania State University \\
College of Information Science and Technology\\ 
University Park, Pennsylvania, USA\\
\mailsa\\
%\mailsb\\
%\mailsc\\
}

%
% NB: a more complex sample for affiliations and the mapping to the
% corresponding authors can be found in the file "llncs.dem"
% (search for the string "\mainmatter" where a contribution starts).
% "llncs.dem" accompanies the document class "llncs.cls".
%

%\toctitle{How People Talk about Armed Conflicts}
%\tocauthor{Jeremy Cole, Ying Xu, and David Reitter}
\maketitle


\begin{abstract}
Armed conflicts around the world produce displacement, injury, and death. 
This study examines how anonymous and quasi-anonymous internet commenters discuss such conflicts.  Specifically, we ask how permissible it is to express positive or negative sentiments about these conflicts as a function of variables including region, conflict nature, and severity. Data from the Armed Conflicts Database is aggregated to identify a number of potential factors that may influence views on acceptable sentiments.  A large-scale sample of the Reddit comment forum was coded for positive and negative sentiments using sentiment analysis techniques. Permissibility is judged using the Reddit voting features. Regressions reveal that positive sentiments are found not permissible depending on the number of fatalities, and that negative sentiments are found permissible for certain regions, more permissible for older conflicts, and more permissible for territorial conflicts.  A number of alternative, non-correlated predictors is presented.

% These results can help disentangle factors such as a conflict’s location from its intensity, which could help explain how people view the multitude of conflicts around the world.
\keywords{Behavioral and Social Sciences; Corpus Linguistics; GLMM; Armed Conflicts; Public Opinion}
\end{abstract}

\input{introduction}
\input{lit}
\input{background}
\input{rq}
%\input{reddit}
\input{methods}
\input{results}
\input{discussion}
\input{futurework}
\input{conclusion}

\bibliographystyle{splncs03}
\bibliography{review,nlp,reddit}


\end{document}
