\section{Reddit Corpus}
To answer our research questions, we chose to use the Reddit corpus. Reddit is a large online internet forum where users are able to discuss a wide array of  topics. To start a discussion, someone submits either a hyperlink or text post. Then, people can reply to these submissions. Users can also reply to the replies to these submissions (and so on). Additionally, users can upvote or downvote both submissions and individual comments. 

In the case of submissions, highly upvoted submissions are more likely to be seen, while highly downvoted submissions are less likely to be seen. Under an individual submission, all comment replies to that submission are sorted by score, and all replies to those comments are sorted by score, and so on. If a comment is sufficiently downvoted, it will be hidden. Hidden comments can still be replied to, upvoted, and downvoted. When a comment receives upvotes and downvotes, it is considered \textit{controversial}.  

Reddit is organized into an infinitely expandable number of smaller forums, normally referred to as subreddits. Each of these subreddits can be about any given topic, general or specific. For instance, it's possible to have a subreddit about science, biology, and genetics. These three subreddits would (or at least could) be completely independent, and they are organized in a flat rather than fashion.

Besides the organizational ways that Reddit is different than Twitter, it also forms something more of a subculture. The vast majority of the discussions (and all discussions we examined) are in English. Over half of the users are in the United States, and the majority are fairly young. 

Our data set consists of approximately two terabytes of Reddit data, ranging from the year 2011 to the year 2014. These comments span every subreddit. 

